Classifying Protein Secondary Structures through Deep Network Learning

### 2013-12-17 docs/paper.tex
first go of paper, done for the night

\subsection{Baseline}

>>>>

\subsection{Baseline}
Because the related works in section \ref{subsec:relatedworks} all used domain knowledge in some form, we developed our own baseline model for comparison to our deep network.
The baseline is a standar neural network using a single hidden layer and trained with back propagation.

\subsubsection{Ensemble of Neural Networks}
The accuracy gained by Rost from the use of an ensemble inspired us to use an ensemble as well.
Unfortunately, due to the time complexity of convergence and limitations of physical compute resources, we were only able to develop this for the simpler baseline neural network.
A majority vote on the outputs of the individual neural networks was used to determine the final output of the ensemble.
